### 2021-04-08 presentations/jsps_2020-03-01/index.Rmd
Update presentation

```{r load-packages, cache = FALSE}
library(magick)
library(gt)
library(ggtext)
library(drake)
library(knitr)
library(patchwork)
library(scales)
library(scico)
library(magrittr)
library(broom)
library(assertr)
library(sf)
library(tidyverse)
```

>>>>

```{r load-packages, cache = FALSE}
library(magick)
library(ggtext)
library(drake)
library(knitr)
library(patchwork)
library(scales)
library(scico)
library(magrittr)
library(broom)
library(assertr)
library(sf)
library(tidyverse)
```
